---
title: "Gandre_Final_project"
author: "Paritosh Gandre"
date: "2023-11-23"
output: pdf_document
---

fontfamily: mathpazo
fontsize: 11pt
header-includes:
   - \linespread{1.05}
urlcolor: blue
---

## libraries:
```{r,echo=FALSE}
library(cowplot)
library(tidyverse)
library(alr4)
library(viridis)
```
## Dataset:
```{r}


NY_data = readr::read_csv("D:/DATA_ANALYTICS/NEW YORK AIR BNB/AB_NYC_2019.csv")
head(NY_data)
ny_clean = NY_data |> na.omit()

```

## Introduction [15 points]

* What research question(s) would you like to answer?

__1__ Distribution of price in different neighbourhood
```{r}
library(ggplot2)

# neighbourhood
top_neighbourhoods = ny_clean |> 
  group_by(neighbourhood) |> 
  summarize(Private = mean(price[room_type == "Private room"]),
            Entire_Home = mean(price[room_type == "Entire home/apt"]),
            Shared_room = mean(price[room_type == "Shared room"])) |> 
  top_n(10, Private) |> 
  arrange(desc(Private))
top_neighbourhoods

top_neighbourhoods_long =top_neighbourhoods |>  pivot_longer(-neighbourhood,names_to = "room_type",values_to = "mean_price") 
top_neighbourhoods_long


ggplot(top_neighbourhoods_long, aes(x = reorder(neighbourhood, -mean_price), y = mean_price, fill = room_type)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
  geom_text(aes(label = sprintf("$%.2f", mean_price)), position = position_dodge(width = 0.9), vjust = -0.5, color = "black", size = 2.5) +
  labs(title = "Top 10 Neighbourhoods: Mean Price by Room Type",x = "Neighbourhood",y = "Mean Price") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "Set3")



```
__2__ How does room type affect price?
```{r}
ny_clean |>
  group_by(room_type)  |> 
  summarize(avg_price = mean(price)) |> 
  ggplot(aes(room_type,avg_price)) +
  geom_bar(stat = "identity") +
  labs(title = "Neighbourhoods with Higher or Lower Prices")+
  theme(axis.text.x = element_text(angle =45, hjust = 1,size = 6)) +
  facet_grid(ny_clean$neighbourhood_group)
  
```

__3__ Neighbourhood with higher or lower price

__4__ Correlation between number of reviews and pricing
```{r}
cor(NY_data$number_of_reviews,NY_data$price)

```

__5__ Does geographic location influence the price of the apartment?

__6__ Areas more costly than others
```{r}
ggplot(NY_data, aes(x = latitude, y = longitude, color = factor(neighbourhood_group))) +
  geom_point(alpha = 0.7, size = 2) +
  scale_color_brewer(palette = "Paired") +
  labs(title = "Geographical Distribution of Points",
       x = "Latitude",
       y = "Longitude")

ggplot(NY_data, aes(x = latitude, y = longitude, fill = log(price))) +
  geom_point(shape = 21, size = 1, color = "black") +
  scale_fill_viridis(option = "plasma", direction = 1) +
  labs(title = "Scatter Plot with Fill by Price",
       x = "Latitude",
       y = "Longitude")


```

* Why a data-driven, computational approach may be useful to answer the questions?
* Describe the dataset that you choose. 

## Computational Methods [30 points]

* For the choosen dataset, what are the necessary data wrangling steps to make the data ready for subsequent analyses?
* What exploratory analyses and modeling techniques can be used to answer the research questions?
* What metrics will be used to evaluate the quality of the data analysis?

## Data Analysis and Results [40 points]

* Perform data analysis, document the analysis procedure, and evaluate the outcomes.
* Present the data analysis results.
* Interpret the results in a way to address the research questions.

## Conclusion [15 points]

* Does the analysis answer the research questions? 
* Discuss the scope and generalizability of the analysis. 
* Discuss potential limitations and possibilities for improvement.
